Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-18 paper_jasa.tex
tiny comments

\begin{table}[hbtp]
\caption{Number of unique subjects and their total feedbacks after applying six screening process on all three experimental data sets. 
\hh{Note that in some of the lines the number of male and female participants does not add up to the total number of participants. This is due to missing demographic information.}}
\begin{center}
\begin{tabular}{rrrrr|rrrr|rrrr}
  \hline
Screening &  \multicolumn{4}{c} {Experiment 1}  & \multicolumn{4}{c} {Experiment 2}  & \multicolumn{4}{c} {Experiment 3} \\
 \cline{2-5}  \cline{6-9}   \cline{10-13}
criteria & Subj & Male & Fem & Total & Subj & Male & Fem & Total & Subj & Male & Fem & Total \\ 
  \hline
1 & 520 & 264 & 201 & 4914 & 390 & 203 & 182 & 4603 & 257 & 166 &  84 & 2830 \\ 
  2 & 465 & 264 & 201 & 4624 & 385 & 203 & 182 & 4558 & 250 & 166 &  84 & 2782 \\ 
  3 & 384 & 200 & 165 & 4187 & 384 & 199 & 181 & 4573 & 227 & 147 &  78 & 2648 \\ 
  4 & 318 & 168 & 135 & 3395 & 378 & 195 & 179 & 4492 & 205 & 133 &  72 & 2393 \\ 
  5 & 277 & 139 & 124 & 3008 & 374 & 193 & 177 & 4451 & 112 &  73 &  39 & 1410 \\ 
  6 & 239 & 121 & 107 & 2317 & 351 & 185 & 164 & 3858 &  98 &  64 &  34 & 1095 \\ 
   \hline
\end{tabular}
\end{center}
\label{tbl:summary}
\end{table}

@@

Yet, it is possible to obtain an estimate the strength of the signal in the actual data plot, when there are multiple evaluations, using Lemma \ref{lemma}. From Equation \ref{fig:pval_plot_signal}  we can write $1 - E[N_m]/K \approx (m-1)E[p_D] $. This gives the signal strength estimate as  
\[
\hat p_D= \frac{1- \frac{u}{K}}{m-1}
\]
where $K$ is the total number of independent evaluations on a lineup and $u$ is the number of successful evaluations. Figure \ref{fig:pval_plot_signal} shows the plot signal strengths in relation with classical test $p$-values. Notice that plot signal strength is equivalent to classical test $p$-value when $p$-value is less than or equal to 0.05 and beyond that the plot signal strength levels off on a point bigger than 0.05. Thus if plot signal strength is less than 0.05, we may decide to reject the null hypothesis.

>>>>

\begin{table}[hbtp]
\caption{Number of unique subjects and their total feedbacks after applying six screening process on all three experimental data sets. 
Note that in some of the lines the number of male and female participants does not add up to the total number of participants. This is due to missing demographic information. \hh{Do we need this table or could we make this a visual comparison? For me, there's too many numbers with too many digits.}}
\begin{center}
\begin{tabular}{rrrrr|rrrr|rrrr}
  \hline
Screening &  \multicolumn{4}{c} {Experiment 1}  & \multicolumn{4}{c} {Experiment 2}  & \multicolumn{4}{c} {Experiment 3} \\
 \cline{2-5}  \cline{6-9}   \cline{10-13}
criteria & Subj & Male & Fem & Total & Subj & Male & Fem & Total & Subj & Male & Fem & Total \\ 
  \hline
1 & 520 & 264 & 201 & 4914 & 390 & 203 & 182 & 4603 & 257 & 166 &  84 & 2830 \\ 
  2 & 465 & 264 & 201 & 4624 & 385 & 203 & 182 & 4558 & 250 & 166 &  84 & 2782 \\ 
  3 & 384 & 200 & 165 & 4187 & 384 & 199 & 181 & 4573 & 227 & 147 &  78 & 2648 \\ 
  4 & 318 & 168 & 135 & 3395 & 378 & 195 & 179 & 4492 & 205 & 133 &  72 & 2393 \\ 
  5 & 277 & 139 & 124 & 3008 & 374 & 193 & 177 & 4451 & 112 &  73 &  39 & 1410 \\ 
  6 & 239 & 121 & 107 & 2317 & 351 & 185 & 164 & 3858 &  98 &  64 &  34 & 1095 \\ 
   \hline
\end{tabular}
\end{center}
\label{tbl:summary}
\end{table}

@@

Yet, it is possible to obtain an estimate the strength of the signal in the actual data plot, when there are multiple evaluations, using Lemma \ref{lemma}. From Equation \ref{fig:pval_plot_signal}  we can write $1 - E[N_m]/K \approx (m-1)E[p_D] $. This gives the signal strength estimate as  
\[
\hat p_D= (1- {u}/{K})/({m-1})
\]
where $K$ is the total number of independent evaluations on a lineup and $u$ is the number of successful evaluations. Figure \ref{fig:pval_plot_signal} shows the plot signal strengths in relation with classical test $p$-values. Notice that plot signal strength is equivalent to classical test $p$-value when $p$-value is less than or equal to 0.05 and beyond that the plot signal strength levels off on a point bigger than 0.05. Thus if plot signal strength is less than 0.05, we may decide to reject the null hypothesis.
